---
title: "Who does more pushups"
author: "Tristyn Thompson"
date: "October 3, 2017"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->






# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->
We can find the answer to our question in two ways: graphing (box and whisker plot) and a numerical result (favstats).

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
The Box and Whisker Plot helps us to identify the difference betweent the two positions.
```{r echo=FALSE}
bwplot(pushups ~ position,
	data = pushups,
	panel = function(..., box.ratio) {
		panel.bwplot(..., fill = NULL, box.ratio = 0.1)
		panel.violin(..., col = "burlywood", border = "grey60", alpha = 0.5, varwidth = FALSE)},
	main = "Who Can Do More Pushups?")
```

The boxes are far apart, we can conclude that there is a huge difference between a line and a skill player. With the violin feature, we can determine the average amount of pushups each position can do.

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
This table identifies the amount of players that could do the specified number of pushups.

```{r echo=FALSE}
favstats(pushups~position, data=pushups)

```

According to this we can determine that skill players can do more pushups than line players by determining the average.

# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

