---
title: "Who does more pushups"
author: "Tristyn Thompson"
date: "October 3, 2017"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the football team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of running and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?

In addition to who does more pushups, we will run a series of tests to show how different line and skill players are.

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

What methods are appropriate for analyzing our data? The choice ofmethod depends on the nature of the vairables involved in the Research Question.

The two variables involved are:

-The position, which is a factor variable with two values ("Line Player" and "Skill Player").
-The amount of pushups, which is also a factor variable, but with two values: "Position" and "Weight"

Both of these variables are numerical. A good graphical method would be a scatter plot. A numerical approach would be to study the relationship between the two numerical values. This can be found by finding the regression line. This is done using the function favstats and T Tests. OF course this will only make sense if the scatterplot shows that the relationship is linear.





# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->
We can find the answer to our question in two ways: graphing (box and whisker plot) and a numerical result (favstats).

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
The Box and Whisker Plot helps us to identify the difference betweent the two positions.
```{r echo=FALSE}
bwplot(pushups ~ position,
	data = pushups,
	panel = function(..., box.ratio) {
		panel.bwplot(..., fill = NULL, box.ratio = 0.1)
		panel.violin(..., col = "burlywood", border = "grey60", alpha = 0.5, varwidth = FALSE)},
	main = "Who Can Do More Pushups?")
```

The boxes are far apart, we can conclude that there is a huge difference between a line and a skill player. With the violin feature, we can determine the average amount of pushups each position can do.


## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
This table identifies the amount of players that could do the specified number of pushups.

```{r echo=FALSE}
favstats(pushups~position, data=pushups)

```

According to this we can determine that skill players can do more pushups than line players by determining the average.







# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r echo=FALSE}
ttestGC(pushups~position, data=pushups)

t.test(pushups~position, data=pushups)
```
Our Null Hypothesis shall be:

$H_0$: There is no relationship between the position of the players and the amount of pushups they can do.

Our Alternative Hypothesis shall be:

$H_0a$: There is a relationship between the position of the players and the amount of pushups they can do.






There is a 95% confidence interval that there is a difference between the two positions.

# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

 

Based on all of these results we can conclude that there is a 95% confidence interval that there is a difference between the two positions. Skill players can do more pushups than line players. Even the average person with basic knowledge of football can conclude the same results. Line players are on the offense and defense and are required to be heavier with a higher body mass. Skill players run around trying to prevent the other team from scoring. They need to run around more than line players meaning, they need to be lighter to be faster. Based on this, a person can conclude that the lighter the body the more pushups a person can do.

